Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-17 manuscript/supplemental_material.Rnw
display the whole human-lineage specific table

<<load.placenta.lineage.specific,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("placenta_lineage_specific")))>>=
load("../data/placenta_lineage_specific")
source("/home/don/projects/xtable/pkg/R/print.xtable.R")

placenta.lineage.specific.table <- function(analysis,output=TRUE) {
    temp.table <- 
        head(placenta.lineage.specific.analysis[analysis.name==analysis &
                                                p.value <= 0.05][order(p.value),
                                                                 list(human_name,p.value,fdr,fc),],
             n=5)
    temp.table <- data.table(temp.table)
    setkey(temp.table,"human_name")
    temp.table <- 
        hugo.nomenclature[temp.table][,list(`Approved Symbol`,
                                            `Approved Name`,p.value,fdr,fc)]
    setnames(temp.table,
              c("Human Symbol","Human Name","p (t-test)","FDR","Fold Change")
              )
    setkey(temp.table,"Human Symbol")
    if (output) {
        display.table <- temp.table[order(`p (t-test)`),]
        display.table <-
            display.table[,`Human Symbol`:=paste0("\\textit{",xtable.sanitize.text(`Human Symbol`),
                                                  "}")]
        print(xtable(display.table,
                     display=c("s","s","s","e","g","f"),
                     ),
              booktabs=TRUE,
              floating=FALSE,
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              include.rownames=FALSE)

@@

\begin{table}[hb]
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{the rodentia order}{all other species}}
\label{tab:rodentia_lineage_specific}
\end{table}

@@

\begin{figure}
<<housekeeping.placenta.distribution,fig.width=8,fig.height=8,out.height="0.8\\textheight",echo=FALSE,message=FALSE>>=
## housekeeping set as apposed to non-housekeeping set
cptg.h <- core.placenta.transcriptome.genes.shape[(human_name %in% housekeeping.genes.superset[,gene_short_name])]

>>>>

<<load.placenta.lineage.specific,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("placenta_lineage_specific")))>>=
load("../data/placenta_lineage_specific")
load("../data/human_mouse_lineage_specific")
source("/home/don/projects/xtable/pkg/R/print.xtable.R")

placenta.lineage.specific.table <- function(analysis,output=TRUE,lineage.table=placenta.lineage.specific.analysis,members=40,orderbyfc=FALSE,fdr.cutoff=1,caption=NULL,label=NULL) {
    temp.table <- 
        lineage.table[analysis.name==analysis &
                      p.value <= 0.05 &
                      fdr <= fdr.cutoff][order(p.value),
                                       list(human_name,p.value,fdr,fc),]
    temp.table <- data.table(temp.table)
    setkey(temp.table,"human_name")
    temp.table <- 
        hugo.nomenclature[temp.table][,list(`Approved Symbol`,
                                            `Approved Name`,p.value,fdr,fc)]
    setnames(temp.table,
              c("Human Symbol","Human Name","p (t-test)","FDR","Fold Change")
              )
    setkey(temp.table,"Human Symbol")
    if (output) {
        display.table <- temp.table[`FDR`<=fdr.cutoff,][order(`p (t-test)`),]
        if (orderbyfc) {
            display.table <- temp.table[order(-abs(`Fold Change`)),]
        }
        if (!is.na(members)) {
            members <- min(c(members,nrow(display.table)))
            display.table <- display.table[1:members,]
        }

        display.table <-
            display.table[,`Human Symbol`:=paste0("\\textit{",xtable.sanitize.text(`Human Symbol`),
                                                  "}")]
        display.table[,`Human Name`:=NULL]
        # setnames(display.table,"Human Symbol","\\multicolumn{1}{p{0.5in}}{Human Symbol}")6
        setnames(display.table,"Fold Change","$\\text{log}_2$ FC")
        print(xtable(display.table,
                     display=c("s","s","e","g","f"),
                     caption=caption,
                     label=label,
                     align=c("c","p{0.7in}","r","r","r")
                     ),
              booktabs=TRUE,
              floating=FALSE,
              tabular.environment=ifelse(is.na(members),"longtable","tabular"),
              math.style.exponents=TRUE,
              sanitize.text.function=genes.table.sanitize,
              size="\\small",
              include.rownames=FALSE)

@@

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption="\\lineagetableexplanationtypeiii{\\human}{all other species}",
                                    label="tab:huamn_linage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

\begin{table}[hb]
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{the rodentia order}{all other species}}
\label{tab:rodentia_lineage_specific}
\end{table}

@@

\begin{figure}
<<housekeeping.placenta.distribution,fig.width=8,fig.height=8,out.height="0.8\\textheight",echo=FALSE,message=FALSE>>=
## housekeeping set as apposed to non-housekeeping set
cptg.h <- core.placenta.transcriptome.genes.shape[(human_name %in% housekeeping.genes.superset[,gene_short_name])]
num.species <- star.logs.wide[,length(unique(species))]

calculate.distribution.shape <- 
    function(min.vector) {
        min.vector <- sort(min.vector,decreasing=TRUE)
        temp <- data.table(FPKM=min.vector,num_genes=1:length(min.vector))
        temp <- temp[order(-num_genes)][!duplicated(FPKM)]
        return(temp)
    }
